\documentclass{article}
\usepackage{amsmath, amssymb}
\usepackage{hyperref, enumitem}
\usepackage[margin=1in]{geometry}

\title{Differential Geometry\\Homework 1}
\date{November 4, 2024}
\author{Rishav}

\begin{document}

\maketitle
\hrule

\section{Open subsets of the real line}
\label{section:one}

Let $\O\neq O\subseteq\mathbb{R}$ be an open connected subset. Prove that $O$ is homeomorphic to $\mathbb{R}$.

\section{Connected components}
\label{section:two}

Let $M$ be a topological space with connected components $\{C_{j}\}_{j\in J}$.

\begin{enumerate}[label=\roman*.]
  \item We declare a subset $O$ of the disjoing union $\bigsqcup_{j\in J}C_{j}$ to be open if $O\cap C_{j}$ if open for all indices $j\in J$. Show that this defines a topology.

  \item Prove that $$M\cong\bigsqcup_{j\in J}C_{j}$$ is a topological space.

  \item Let $N$ be another topological space with connected components $\{C'_{j}\}_{j\in J'}$. Conclude that the spaces $M$ and $N$ are homeomorphic iff there is a bijection $$\phi:J\rightarrow J'$$ such that $$C_{j}\cong C'_{\phi(j)}\quad\text{for all }j\in J.$$
\end{enumerate}

\section{The Lindelöf property}

Let $M$ be a second countable topologival space. Recall that an open covering $\{U_{\alpha}\}_{\alpha\in J}$ of $M$ is a collection of open subsets $U_{\alpha}\subseteq M$ such that $$M=\bigcup_{\alpha\in J}U_{\alpha}.$$

\begin{enumerate}[label=\roman*.]
  \item Prove that every open covering of $M$ admits a countable subcover.

  {\footnotesize Hint: Do not spoil yourself and prove this on your own.}

  \item Does the converse of above hold?
\end{enumerate}

\section{Classification of 1-manifolds}

Consider the unit circle $$\mathbb{S}^{1}:=\{z\in\mathbb{C}:|z|=1\}$$ endowed with the subspace topology inherited from $\mathbb{C}$. The goal of this exercise if to prove that every connected topological manifold of dimension one is homeomorphic to $\mathbb{R}$ or $\mathbb{S}^{1}$. By virtue of Exercise \ref{section:two} this already suffices to classify all topological 1-manifolds.

\begin{enumerate}[label=\roman*.]
  \item Show that $\mathbb{S}^{1}$ is a topological manifold, which is not homeomorphic to $\mathbb{R}$.
\end{enumerate}

Let $M$ be a connected topological 1-manifold such that there exists open subsets $O_{1}, O_{2}\subseteq M$ covering $M$ such that $O_{1}\cong\mathbb{R}\cong O_{2}$.

\begin{enumerate}[label=\roman*., start=3]
  \item Assume moreover that the intersection $O_{1}\cup O_{2}$ is connected. Probe that $M$ is homeomorphic to $\mathbb{R}$.

  {\footnotesize Hint: Study the image of $M\backslash O_{2}$ under the homeomorphism $\phi_{1}:O_{1}\rightarrow\mathbb{R}$. Choose a point $p_{0}\in O_{1}\cap O_{2}$ and glue the homeomorphisms $\phi_{1}$ and $\phi_{2}:O_{2}\rightarrow\mathbb{R}$ at $p_{0}$.} 

  \item Assume now that the intersection $O_{1}\cup O_{2}$ is disconnected. Prove that $M$ is homeomorphic to $\mathbb{S}^{1}$.

  {\footnotesize First assert that this means that $O_{1}\cup O_{2}$ has precisely two connected components. Afterwards, you can either mimic the proof of ii or consider $M\backslash\{p_{0}\}$ for a suitably chosen point $p_{0}\in O_{1}\cup O_{2}$. Use what you have already shown to conclude $M\backslash\{p_{0}\}\cong\mathbb{R}$ and construct a homeomorphism between $M$ and $\mathbb{S}^{1}$ from this insight.}

  \item Let now $M$ be a topological space admitting an open covering $\{O_{n}\}_{n\in N}$ such that $$O_{m}\subseteq O_{n+1}\quad\text{and}\quad O_{n}\cong\mathbb{R}$$ for all $n\in\mathbb{N}$. Show that $M\cong\mathbb{R}$.

  {\footnotesize Hint: Utilize the consderable freedom Exercise \ref{section:one} affords you.}

  \item Conclude that every connected topological 1-manifold is homeomorphic to $\mathbb{R}$ or $\mathbb{S}^{1}$.
\end{enumerate}
\end{document}
